The Globular Cluster System of the Auriga Simulations

### 2019-06-05 AurigaGCS.tex
Introduction

% Abstract of the paper
\begin{abstract}
We investigate whether the galaxy formation model used for the Auriga simulations
can produce a realistic globular cluster population at redshift zero. We compare
properties of the simulated star particles in the Auriga haloes with catalogues 
of observations of the Milky Way and Andromeda globular cluster populations available
in the literature. We find that the Auriga simulations do produce sufficient mass
at radii and metallicities that are typical for the MW GCS, although we observe
a varying mass-excess for the different $R_{\text{GC}}$-[Fe/H] bins. This implies
different values for the combined product of the bound cluster formation efficiency
and the globular cluster disruption rate. Furthermore we test whether any of the
Auriga galaxies has a metallicity and radial distribution that is consistent with
the MW (M31) GCS. For all of the Auriga haloes we reject the null hypothesis that
the simulated and observed metallicities are drawn from the same distribution at
$\geq98.32$~\% confidence level, for the GCS of the Milky Way as well as that of
the Andromeda galaxy. The same holds true for the distribution of galactocentric 
radius. Overall, the Auriga simulations produce old star particles with higher
metallicities than the MW and M31 GCS and at larger radii. The formation efficiency
would have to linearly decrease with increasing metallicity for the Auriga GC
candidates to be consistent with the MW GCS.
\end{abstract}

@@

\section{Introduction}
Globular clusters (GC)s are omnipresent, bright, old, and amongst the simplest
stellar configurations in the Universe. The GC system of the Milky Way (MW) consists
of $\sim$160 GCs, most of which are older than $\sim$10~Gyr, and the Andromeda 
galaxy (M31) hosts roughly twice as many GCs with ages $\geq 6$~Gyr. With masses of 
$10^{4-6}$ M\Sun within typical half-mass radii of a few parsec, the combined stellar 
light emitted by GCs makes it possible to obtain integrated properties within the Local
Group with reasonable certainty, and even allows for observations beyond the Local Group 
\citep[e.g.][]{1991ARA&A..29..543H}. The extensive literature on GCs is summarised in
several books and review articles \citep[e.g.][]{Harris2001, 2004Natur.427...31W, 
2006ARA&A..44..193B, 2012A&ARv..20...50G, 2014CQGra..31x4006K, 2018RSPSA.47470616F}, and
recent analyses of the Gaia data shed new light on the chemical- and structural properties,
and on the phase-space distribution of the MW GC system \citep[e.g.][]{2018A&A...616A..12G, 
2018ApJ...859L..13B, 2019A&A...621A..56P, 2019MNRAS.484.2832V}.

\todo[inline]{Correlations between GC systems and their host galaxies}
The natal gas regions in which globular clusters form inherit key characteristics 
from their parent (proto-)galaxies. GC populations, in turn, will therefore retain 
a record of these properties and offer unique insight into the detailed chemical 
and dynamical evolution history of their host galaxies \citep[see][for a recent review]
{2006ARA&A..44..193B}. In theory, this information should be readily available
and easily observable in the low redshift Universe, given that GCs survive nearly
a Hubble time of evolution within the violent galactic environments they live in. 
However, these long and complex evolution histories themselves impose their
imprints onto the GCs observables. Thus, a prerequisite to infer galactic histories
from studies of GC systems is to understand the subtleties of the GC formation
and evolution itself.

>>>>

% Abstract of the paper
\begin{abstract}
We investigate whether the galaxy formation model used for the Auriga simulations
can produce a realistic globular cluster population at redshift zero. We compare
properties of the simulated star particles in the Auriga haloes with catalogues
of observations of the Milky Way and Andromeda globular cluster populations available
in the literature. We find that the Auriga simulations do produce sufficient mass
at radii and metallicities that are typical for the MW GCS, although we observe
a varying mass-excess for the different $R_{\text{GC}}$-[Fe/H] bins. This implies
different values for the combined product of the bound cluster formation efficiency
and the globular cluster disruption rate. Furthermore we test whether any of the
Auriga galaxies has a metallicity and radial distribution that is consistent with
the MW (M31) GCS. For any one of the Auriga haloes we reject the null hypothesis that
the simulated and observed metallicities are drawn from the same distribution at
$\geq98.32$~\% confidence level, for the GCS of the Milky Way as well as that of
the Andromeda galaxy. The same holds true for the distribution of galactocentric
radius. Overall, the Auriga simulations produce old star particles with higher
metallicities than the MW and M31 GCS and at larger radii. The formation efficiency
would have to linearly decrease with increasing metallicity for the Auriga GC
candidates to be consistent with the MW GCS.
\end{abstract}

@@

\section{Introduction}
Globular clusters (GC)s are omnipresent, bright (with ${<}M^0_V{>} = -7.1 \pm 0.4$
that is nearly independent of the host galaxy size and environment,
\citealt{1991ARA&A..29..543H}), old ($\gtrsim$10~Gyr, \citealt{2005A&A...439..997P,
2005AJ....130.1315S, 2009ApJ...694.1498M, 2013ApJ...775..134V}), and amongst the
simplest stellar configurations in the Universe. The typical luminosity gives
a characteristic mass of $1.4\cdot 10^5$~M\Sun \, (assuming a mass to light ratio
$M/L_V \simeq 2$), and GCs have typical half-mass radii $r_h$ of a few parsec.
GCs within the Milky Way can thus be studied in great detail (at the level of 
individual stars), whereas integrated quantities can be explored with reasonable 
certainty for GCs within - and even beyond \citep[e.g.][]{1991ARA&A..29..543H} -
the Local Group.

The extensive literature on GCs is summarised in several 
books and review articles \citep[e.g.][]{1991ARA&A..29..543H, Harris2001, 2004Natur.427...31W, 
2006ARA&A..44..193B, 2012A&ARv..20...50G, 2014CQGra..31x4006K, 2018RSPSA.47470616F},
and recent analyses of the Gaia data shed new light on the chemical- and structural 
properties, and on the phase-space distribution of the MW GC system \citep[e.g.][]{
2018A&A...616A..12G, 2018ApJ...859L..13B, 2019A&A...621A..56P, 2019MNRAS.484.2832V}.
A clear picture of the formation GC systems has yet to emerge, despite decades 
of studies and the tremendous advances the last couple of years. It is clear, 
however, that a fundamental understanding of GC formation and evolution promises 
exciting insight into the detailed histories of their host galaxies due to their
old ages and several correlations between GC systems and their parent galaxies.

% There are several correlations between globular cluster systems and their
% host galaxy. For example, the total mass of globular cluster systems
% correlates with the halo mass \citep[e.g.][]{2010MNRAS.406.1967G}, the
% the total number of GCs increases linearly with increasing virial mass
% \citep[e.g.][]{2019arXiv190100900B}, and THIRD EXAMPLE.
